### 2016-06-29 store-consistency.tex

First, we focus on the sequential aspect of the proof and show that
the assertions that decorate \C{Wd1} are indeed valid. We consider the
triple associated with the assignment to \C{C} for illustration. The
precondition $\phi_4$ asserts different values for \C{C} and \C{v3}
(temporary alias of RHS expression) depending on whether or not
\C{Wd2} is committed. Inside \C{Wd1}, $\committed(\C{Wd2})$ may mean
that either \C{Wd2} happened before \C{Wd1} (hence can be visible to
all of \C{Wd1}), or that it committed concurrently with \C{Wd1} (hence
cannot be visible to all of \C{Wd2}).  Nonetheless, $\phi_4$ only
considers the case when $\C{Wd2} \visar \C{Wd1}$. As we show below,
this is sufficient to prove the postcondition $\phi_5$, which appears
to make a stronger claim about the value of \C{C}. The proof follows
from the RG rule \rulelabel{RG-Asgn} for assignments, which allows us
to easiliy conclude the following about the execution state after the
assignment:
\begin{smathpar}
\begin{array}{l}
    {\neg\committed(\C{Wd1}) \conj \C{Wd1} \wrstoar \C{C} 
    \conj (\neg\committed(\C{Wd2})} \Rightarrow \C{C = k-a1}) \conj\\
    ({\committed(\C{Wd2})} \Rightarrow \C{Wd2} \wrstoar
    \C{C}) \conj \\
    ({\committed(\C{Wd2})} \wedge {\C{Wd2} \visar \C{Wd1}} 
    \Rightarrow \C{C = k-a2} \wedge \C{C = k-a2-a1})
\end{array}
\end{smathpar}
The rule also lets us assume that the execution satisfies trace
invariant ($\I$), which asserts {\sc si} for both transactions.  Since
both transactions now write to \C{C}, {\sc si} requires either
$\C{Wd1} \visar \C{Wd2}$, or $\C{Wd2} \visar \C{Wd1}$. Since \C{Wd1}
is not yet committed ($\neg\committed(\C{Wd1})$), {\sc si} (which
subsumes {\sc rc}) prohibits the former possibility, allowing us the
deduce $\C{Wd2} \visar \C{Wd1}$. This lets us derive
${\committed(\C{Wd2})}  \Rightarrow \C{C = k-a2} \wedge \C{C =
k-a2-a1}$, allowing us to prove the postcondition $\phi_5$.

@@

\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{C} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{C=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{C=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{C} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{C=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{C} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}
For the sake of completeness, we also explicitly represent the fact
that all the effects added by $R_1$ are of \C{Wd2}. This is
needed to prove that an interference from \C{Wd2} does effect the
local state of \C{Wd1}.

>>>>

First, we focus on the sequential aspect of the proof and show that
the assertions that decorate \C{Wd1} are indeed valid. We consider the
triple associated with the assignment to \C{C} for illustration. The
precondition $\phi_4$ asserts different values for \C{C} and \C{v3}
(temporary alias of RHS expression) depending on whether or not
\C{Wd2} is committed. Inside \C{Wd1}, $\committed(\C{Wd2})$ may mean
that either \C{Wd2} happened before \C{Wd1} (hence can be visible to
all of \C{Wd1}), or that it committed concurrently with \C{Wd1} (hence
cannot be visible to all of \C{Wd2}).  Nonetheless, $\phi_4$ only
considers the case when $\C{Wd2} \visar \C{Wd1}$. As we show below,
this is sufficient to prove the postcondition $\phi_5$, which appears
to make a stronger claim about the value of \C{C}. The proof follows
from the RG rule \rulelabel{RG-Asgn} for assignments, which allows us
to easiliy conclude the following about the execution state after the
assignment:
>>>>>>> 70ae6b11c8f648c323413d6fe8f8fb1c2cba75ae
\begin{smathpar}
\begin{array}{l}
    {\neg\committed(\C{Wd1}) \conj \C{Wd1} \wrstoar \C{C} 
    \conj (\neg\committed(\C{Wd2})} \Rightarrow \C{C = k-a1}) \conj\\
    ({\committed(\C{Wd2})} \Rightarrow \C{Wd2} \wrstoar
    \C{C}) \conj \\
    ({\committed(\C{Wd2})} \wedge {\C{Wd2} \visar \C{Wd1}} 
    \Rightarrow \C{C = k-a2} \wedge \C{C = k-a2-a1})
\end{array}
\end{smathpar}

\noindent The rule also lets us assume that the execution satisfies trace
invariant ($\I$), which asserts {\sc si} for both transactions.  Since
both transactions now write to \C{C}, {\sc si} requires either
$\C{Wd1} \visar \C{Wd2}$, or $\C{Wd2} \visar \C{Wd1}$. Since \C{Wd1}
is not yet committed ($\neg\committed(\C{Wd1})$), {\sc si} (which
subsumes {\sc rc}) prohibits the former possibility, allowing us the
deduce $\C{Wd2} \visar \C{Wd1}$. This lets us derive
${\committed(\C{Wd2})}  \Rightarrow \C{C = k-a2} \wedge \C{C =
k-a2-a1}$, allowing us to prove the postcondition $\phi_5$.

@@

\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{C} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{C=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{C=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{C} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{C=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{C} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}
For the sake of completeness, we also explicitly represent the fact
that all the effects added by $R_1$ are of \C{Wd2}. This is needed to
prove that an interference from \C{Wd2} does not affect the local
state of \C{Wd1}.
